### 2020-10-08 serial.tex
edit

Since generation intervals measure time between infection events, which can be difficult to observe in practice, generation intervals are often replaced with serial intervals.
The serial interval is defined as the time between when an infector and an infectee develop symptoms \citep{svensson2007note}.
While generation and serial intervals both measure the time scale of disease transmission, they measure fundamentally different quantities. 
In particular, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence}.
Serial intervals can in some cases even take negative values in the presence of presymptomatic transmission \citep{he2020temporal}, whereas generation intervals must be positive.

>>>>

Since generation intervals measure time between infection events, which can be difficult to observe in practice, generation intervals are often replaced with serial intervals.
The serial interval is defined as the time between when an infector and an infectee develop symptoms \citep{svensson2007note}.
While generation and serial intervals both measure the time scale of disease transmission, they measure fundamentally different quantities. 
In particular, previous studies have noted that, in many contexts, serial intervals are expected to have larger variances than generation intervals but have the same mean when the incubation periods of the infector and infectee are identically distributed \citep{svensson2007note,klinkenberg2011correlation,te2013estimating,champredon2018equivalence}.
Serial intervals can in some cases even take negative values in the presence of presymptomatic transmission \citep{he2020temporal}, whereas generation intervals must be positive.
